Lyman-$\alpha$ photons through rotating outflows

### 2018-03-29 paper/paper.tex
edit

The quality of the results from the Doppler boos improves for higher
\tauh values. 
In the Appendix we show the same plots as Figures
\ref{fig:doppler_shift} and \ref{fig:doppler_shift}, there it is
evident that for $\tauh=10^5$ the results are not as good as they are
for $\tauh=10^6$, and that for $\tauh=10^7$ the Doppler boos
provides a remarkable good approximation.

@@

\begin{equation}
\label{eq:bi}
\mathrm{BI} = \mathrm{KURTOSIS} - \mathrm{SKW}^2 = \frac{m_4}{m_2^{2}} - \frac{m_3^2}{m_2^{3}},
\end{equation}
%
where each $m_i$ is the i-th moment about the mean. 
The STD has velocity units and quantifies the dispersion of the line's
velocity: the larger it is, the wider the line.  
The SKW is adimensional and quantifies the peaks' asymmetry. 
In the case of a bimodal distributio 
$SKW>0$ the blue peak is taller and for $SWK<0$ the right peak is
taller. The BI is adimensional and quantifies if the line has 1 or 2 peaks: it is  always $\geq 1$ \citep{Pearson1929} and the closer it is to 1, the more bimodal is the line (i.e. has 2 peaks).

>>>>

The quality of the results from the Doppler boost improves for higher
\tauh values. 
In the Appendix we show the same plots as Figures
\ref{fig:doppler_shift} and \ref{fig:doppler_shift}, there it is
evident that for $\tauh=10^5$ the results are not as good as they are
for $\tauh=10^6$, and that for $\tauh=10^7$ the Doppler boos
provides a remarkable good approximation.

@@

\begin{equation}
\label{eq:bi}
\mathrm{BI} = \mathrm{KURTOSIS} - \mathrm{SKW}^2 = \frac{m_4}{m_2^{2}} - \frac{m_3^2}{m_2^{3}},
\end{equation}
%
where each $m_i$ is the i-th moment about the mean. 
The STD has velocity units and quantifies the line's width.
The SKW is adimensional and quantifies the peaks' asymmetry. 
In the case of a bimodal distribution, $SKW>0$ means that the blue
peak is taller and for $SWK<0$ the red peak is taller. 
The BI is adimensional and quantifies whether the line has 1 or 2
peaks: it is  always $\geq 1$ \citep{Pearson1929} and the 
to 1, the more bimodal is the line (i.e. has 2 similar peaks). 
We found by visual inspection of our spectra that BI$=2.5$ marks the
transition between two peaks (however imbalanced) and a dominang
single peak.
